\textbf{\sc Towards Deliberative Control of Autonomous Robots}

### 2012-02-07 trunk/intro.tex
updates

We have developed, tested and deployed the Teleo-Reactive EXecutive
(\texttt{T-REX}) an on-board adaptive control system that integrates
AI based planning and probabilistic state estimation in a hybrid
executive \cite{mcgann08a,mcgann08b,Py10}.  Probabilistic state
estimation integrates a number of science observations to produce a
likelihood that the vehicle sensors perceive a feature of
interest. Onboard planning and execution enables adaptation of
navigation and instrument control based on the probability of having
detected such a phenomenon. It further enables goal-directed
commanding within the context of projected mission state and allows
for replanning for off-nominal situations and opportunistic science
events. The framework in addition to being used on an AUV, is general
enough be used for controlling a personal robot \cite{mcgann2009} and
is deployed on a European planetary rover testbed
\cite{goac11}. Probabilistic state estimation is discussed elsewhere
\cite{mcgann08d} and out of scope for this chapter. Deliberation and
reaction are integrated systematically over different temporal and
functional scopes within a single agent and a single model that covers
the needs of high-level mission management, low-level navigation,
instrument control, and detection of unstructured and poorly
understood phenomena. \rx is deployed on MBARI's Dorado AUV shown in
Fig. \ref{fig:auv-fig}, which to the best of our knowledge is the only
operational marine platform anywhere being used for routine scientific
surveys with onboard plan synthesis.

>>>>

We have developed, tested and deployed the Teleo-Reactive EXecutive
(\texttt{T-REX}) an on-board adaptive control system that integrates
AI based planning and probabilistic state estimation in a hybrid
executive \cite{mcgann08a,mcgann08b,py10}.  Probabilistic state
estimation integrates a number of science observations to produce a
likelihood that the vehicle sensors perceive a feature of
interest. Onboard planning and execution enables adaptation of
navigation and instrument control based on the probability of having
detected such a phenomenon. It further enables goal-directed
commanding within the context of projected mission state and allows
for replanning for off-nominal situations and opportunistic science
events. The framework in addition to being used on an AUV, is general
enough be used for controlling a personal robot \cite{mcgann2009} and
is deployed on a European planetary rover testbed
\cite{goac11}. Probabilistic state estimation is discussed elsewhere
\cite{mcgann08d} and out of scope for this chapter. Deliberation and
reaction are integrated systematically over different temporal and
functional scopes within a single agent and a single model that covers
the needs of high-level mission management, low-level navigation,
instrument control, and detection of unstructured and poorly
understood phenomena. \rx is deployed on MBARI's Dorado AUV shown in
Fig. \ref{fig:auv-fig}, which to the best of our knowledge is the only
operational marine platform anywhere being used for routine scientific
surveys with onboard plan synthesis.
